---
title: "ERGM Fitting"
output: ergmfitting
---

Code adapted from Chapter 6 of "Statistical Analysis of Network Data in R" by Kolacsyk and Csardi and https://gvegayon.github.io/appliedsnar/the-ergm-package.html. 

Load necessary packages.

```{r}
library(ergm)
library(intergraph)
```

Convert igraph network "net1" to network object.

```{r}
network_influence <- intergraph::asNetwork(net1)

# Running a simple ergm (only fitting edge count)
ergm(network_influence ~ edges)
```
Add vertex attributes to network graph.

```{r}
network::set.vertex.attribute(network_influence, "Genre",
                              data_by_artist_with_genre$artist_genre)
network::set.vertex.attribute(network_influence, "Danceability",
                              data_by_artist_with_genre$danceability)
network::set.vertex.attribute(network_influence, "Energy",
                              data_by_artist_with_genre$energy)
network::set.vertex.attribute(network_influence, "Loudness",
                              data_by_artist_with_genre$loudness)
network::set.vertex.attribute(network_influence, "Valence",
                              data_by_artist_with_genre$valence)
network::set.vertex.attribute(network_influence, "Tempo",
                              data_by_artist_with_genre$tempo)
network::set.vertex.attribute(network_influence, "Key",
                              data_by_artist_with_genre$key)
network::set.vertex.attribute(network_influence, "Acousticness",
                              data_by_artist_with_genre$acousticness)
network::set.vertex.attribute(network_influence, "Instrumentalness",
                              data_by_artist_with_genre$instrumentalness)
network::set.vertex.attribute(network_influence, "Liveness",
                              data_by_artist_with_genre$liveness)
network::set.vertex.attribute(network_influence, "Speechiness",
                              data_by_artist_with_genre$speechiness)
network::set.vertex.attribute(network_influence, "Duration",
                              data_by_artist_with_genre$duration_ms)
network::set.vertex.attribute(network_influence, "ActiveStart",
                              data_by_artist_with_genre$active_start)
```


Create Bernoulli random graph model.

```{r}
my.ergm.bern <- formula(network_influence ~ edges)
my.ergm.bern
summary(my.ergm.bern)
#degreedist(network_influence)
```


Fit ERGMs using vertex characteristics. Add characteristics individually.

```{r}
network_influence1d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Danceability"))

set.seed(42)
network_influence.ergm1d.fit <- ergm(network_influence1d.ergm)
```
```{r}
anova(network_influence.ergm1d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm1d.fit)
```

```{r}
network_influence2d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Danceability")
                       + nodeicov("Energy"))

set.seed(42)
network_influence.ergm2d.fit <- ergm(network_influence2d.ergm)
```

```{r}
anova(network_influence.ergm2d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm2d.fit)
```
```{r}
network_influence3d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy"))

set.seed(42)
network_influence.ergm3d.fit <- ergm(network_influence3d.ergm)
```

```{r}
anova(network_influence.ergm3d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm3d.fit)
```

```{r}
network_influence4d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence"))

set.seed(42)
network_influence.ergm4d.fit <- ergm(network_influence4d.ergm)
```

```{r}
anova(network_influence.ergm4d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm4d.fit)
```

```{r}
network_influence5d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo"))

set.seed(42)
network_influence.ergm5d.fit <- ergm(network_influence5d.ergm)
```
```{r}
anova(network_influence.ergm5d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm5d.fit)
```

```{r}
network_influence6d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness"))

set.seed(42)
network_influence.ergm6d.fit <- ergm(network_influence6d.ergm)
```

```{r}
anova(network_influence.ergm6d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm6d.fit)
```


```{r}
network_influence7d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness"))

set.seed(42)
network_influence.ergm7d.fit <- ergm(network_influence7d.ergm)
```

```{r}
anova(network_influence.ergm7d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm7d.fit)
```


```{r}
network_influence8d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness"))

set.seed(42)
network_influence.ergm8d.fit <- ergm(network_influence8d.ergm)
```

```{r}
anova(network_influence.ergm8d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm8d.fit)
```


```{r}
network_influence9d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness")
                       + nodeicov("Speechiness"))

set.seed(42)
network_influence.ergm9d.fit <- ergm(network_influence9d.ergm)
```

```{r}
anova(network_influence.ergm9d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm9d.fit)
```


```{r}
network_influence10d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness")
                       + nodeicov("Speechiness")
                       + match("Genre"))

set.seed(42)
network_influence.ergm10d.fit <- ergm(network_influence10d.ergm)
```
```{r}
anova(network_influence.ergm10d.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm10d.fit)
```
```{r}
network_influence11d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness")
                       + nodeicov("Speechiness")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm11d.fit <- ergm(network_influence11d.ergm)
```

```{r}
anova(network_influence.ergm11d.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm11d.fit)
```
```{r}
gof.network.ergm11d <- gof(network_influence.ergm11d.fit)

plot(gof.network.ergm11d)
```
```{r}
gof.network.ergm11d
```


```{r}
network_influence12d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness")
                       + nodeicov("Speechiness")
                       + nodeicov("Key")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm12d.fit <- ergm(network_influence12d.ergm)
```

```{r}
anova(network_influence.ergm12d.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm12d.fit)
```

Model 12 directed is worse than model 11 directed. We should not include Key as an in-degree covariate. 

```{r}
network_influence13d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness")
                       + nodeicov("Speechiness")
                       + nodefactor("Genre")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm13d.fit <- ergm(network_influence13d.ergm)
```

```{r}
anova(network_influence.ergm13d.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm13d.fit)
```


```{r}
gof.network.ergm13d <- gof(network_influence.ergm13d.fit)

plot(gof.network.ergm13d)

summary(gof.network.ergm13d)

```
```{r}
gof.network.ergm13d
```


```{r}
network_influence14d.ergm <- formula(network_influence ~ edges
                       + match("Genre"))

set.seed(42)
network_influence.ergm14d.fit <- ergm(network_influence14d.ergm)
```


```{r}
anova(network_influence.ergm14d.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm14d.fit)
```
```{r}
gof.network.ergm14d <- gof(network_influence.ergm14d.fit)

plot(gof.network.ergm14d)
```
```{r}
gof.network.ergm14d
```

```{r}
network_influence15d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness")
                       + nodeicov("Speechiness")
                       + nodematch("Key"))

set.seed(42)
network_influence.ergm15d.fit <- ergm(network_influence15d.ergm)
```
```{r}
anova(network_influence.ergm15d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm15d.fit)
```

```{r}
gof.network.ergm15d <- gof(network_influence.ergm15d.fit)

plot(gof.network.ergm15d)
```
```{r}
network_influence16d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness")
                       + nodeicov("Speechiness")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm16d.fit <- ergm(network_influence16d.ergm)
```


```{r}
anova(network_influence.ergm16d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm16d.fit)
```

```{r}
gof.network.ergm16d <- gof(network_influence.ergm16d.fit)

plot(gof.network.ergm16d)
```
```{r}
gof.network.ergm16d
```

```{r}
network_influence17d.ergm <- formula(network_influence ~ edges
                       + nodeicov("Loudness")
                       + nodeicov("Danceability")
                       + nodeicov("Energy")
                       + nodeicov("Valence")
                       + nodeicov("Tempo")
                       + nodeicov("Acousticness")
                       + nodeicov("Instrumentalness")
                       + nodeicov("Liveness")
                       + nodeicov("Speechiness")
                       + nodeicov("Duration")
                       + nodeicov("ActiveStart")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm17d.fit <- ergm(network_influence17d.ergm)
```

```{r}
anova(network_influence.ergm17d.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm17d.fit)
```

```{r}
gof.network.ergm17d <- gof(network_influence.ergm17d.fit)

plot(gof.network.ergm17d)
```

```{r}
gof.network.ergm17d
```

