---
title: "ERGM Fitting"
output: ergmfitting
---

Code adapted from Chapter 6 of "Statistical Analysis of Network Data in R" by Kolacsyk and Csardi and https://gvegayon.github.io/appliedsnar/the-ergm-package.html. 

Load necessary packages.

```{r}
library(ergm)
library(intergraph)
```

Convert igraph network "net1" to network object.

```{r}
network_influence <- intergraph::asNetwork(net1)

# Running a simple ergm (only fitting edge count)
ergm(network_influence ~ edges)
```
Add vertex attributes to network graph.

```{r}
network::set.vertex.attribute(network_influence, "Genre",
                              data_by_artist_with_genre$artist_genre)
network::set.vertex.attribute(network_influence, "Danceability",
                              data_by_artist_with_genre$danceability)
network::set.vertex.attribute(network_influence, "Energy",
                              data_by_artist_with_genre$energy)
network::set.vertex.attribute(network_influence, "Loudness",
                              data_by_artist_with_genre$loudness)
network::set.vertex.attribute(network_influence, "Valence",
                              data_by_artist_with_genre$valence)
network::set.vertex.attribute(network_influence, "Tempo",
                              data_by_artist_with_genre$tempo)
network::set.vertex.attribute(network_influence, "Key",
                              data_by_artist_with_genre$key)
network::set.vertex.attribute(network_influence, "Acousticness",
                              data_by_artist_with_genre$acousticness)
network::set.vertex.attribute(network_influence, "Instrumentalness",
                              data_by_artist_with_genre$instrumentalness)
network::set.vertex.attribute(network_influence, "Liveness",
                              data_by_artist_with_genre$liveness)
network::set.vertex.attribute(network_influence, "Speechiness",
                              data_by_artist_with_genre$speechiness)
network::set.vertex.attribute(network_influence, "Duration",
                              data_by_artist_with_genre$duration_ms)
network::set.vertex.attribute(network_influence, "ActiveStart",
                              data_by_artist_with_genre$active_start)
```


Create Bernoulli random graph model.

```{r}
my.ergm.bern <- formula(network_influence ~ edges)
my.ergm.bern
summary(my.ergm.bern)
#degreedist(network_influence)
```


Fit ERGMs using vertex characteristics. Add characteristics individually.

ERGM with characteristic danceability:

```{r}
network_influence1.ergm <- formula(network_influence ~ edges
                       + nodemain("Danceability"))

set.seed(42)
network_influence.ergm1.fit <- ergm(network_influence1.ergm)
```
```{r}
anova(network_influence.ergm1.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm1.fit)
```

ERGM with characteristics danceability and energy:

```{r}
network_influence2.ergm <- formula(network_influence ~ edges
                       + nodemain("Danceability")
                       + nodemain("Energy"))

set.seed(42)
network_influence.ergm2.fit <- ergm(network_influence2.ergm)
```

ERGM with characteristics danceability, loudness, energy:

```{r}
anova(network_influence.ergm2.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm2.fit)
```
```{r}
network_influence3.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy"))

set.seed(42)
network_influence.ergm3.fit <- ergm(network_influence3.ergm)
```

```{r}
anova(network_influence.ergm3.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm3.fit)
```

ERGM with characteristics loudness, danceability, energy, valence:

```{r}
network_influence4.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence"))

set.seed(42)
network_influence.ergm4.fit <- ergm(network_influence4.ergm)
```

```{r}
anova(network_influence.ergm4.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm4.fit)
```

ERGM with characteristics loudness, danceability, energy, valence, tempo:

```{r}
network_influence5.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo"))

set.seed(42)
network_influence.ergm5.fit <- ergm(network_influence5.ergm)
```
```{r}
anova(network_influence.ergm5.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm5.fit)
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness:

```{r}
network_influence6.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness"))

set.seed(42)
network_influence.ergm6.fit <- ergm(network_influence6.ergm)
```

```{r}
anova(network_influence.ergm6.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm6.fit)
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness:

```{r}
network_influence7.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness"))

set.seed(42)
network_influence.ergm7.fit <- ergm(network_influence7.ergm)
```

```{r}
anova(network_influence.ergm7.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm7.fit)
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness, liveness:

```{r}
network_influence8.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness")
                       + nodemain("Liveness"))

set.seed(42)
network_influence.ergm8.fit <- ergm(network_influence8.ergm)
```

```{r}
anova(network_influence.ergm8.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm8.fit)
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness, liveness, speechiness:

```{r}
network_influence9.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness")
                       + nodemain("Liveness")
                       + nodemain("Speechiness"))

set.seed(42)
network_influence.ergm9.fit <- ergm(network_influence9.ergm)
```

```{r}
anova(network_influence.ergm9.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm9.fit)
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness, liveness, speechiness, genre matching:

```{r}
network_influence10.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness")
                       + nodemain("Liveness")
                       + nodemain("Speechiness")
                       + match("Genre"))

set.seed(42)
network_influence.ergm10.fit <- ergm(network_influence10.ergm)
```


```{r}
anova(network_influence.ergm10.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm10.fit)
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness, liveness, speechiness, genre matching, key matching:

```{r}
network_influence11.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness")
                       + nodemain("Liveness")
                       + nodemain("Speechiness")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm11.fit <- ergm(network_influence11.ergm)
```

```{r}
anova(network_influence.ergm11.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm11.fit)
```



```{r}
gof.network.ergm11 <- gof(network_influence.ergm11.fit)

plot(gof.network.ergm11)

gof.network.ergm11
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness, liveness, speechiness, key, genre matching, key matching:

```{r}
network_influence12.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness")
                       + nodemain("Liveness")
                       + nodemain("Speechiness")
                       + nodemain("Key")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm12.fit <- ergm(network_influence12.ergm)
```

```{r}
anova(network_influence.ergm12.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm12.fit)
```


```{r}
gof.network.ergm12 <- gof(network_influence.ergm12.fit)

plot(gof.network.ergm12)

gof.network.ergm12

```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness, liveness, speechiness, key, genre, genre matching, key matching:

```{r}
network_influence13.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness")
                       + nodemain("Liveness")
                       + nodemain("Speechiness")
                       + nodemain("Key")
                       + nodefactor("Genre")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm13.fit <- ergm(network_influence13.ergm)
```


```{r}
anova(network_influence.ergm13.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm13.fit)
```

```{r}
gof.network.ergm13 <- gof(network_influence.ergm13.fit)

plot(gof.network.ergm13)

gof.network.ergm13
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness, liveness, speechiness, key, duration, genre, genre matching, key matching:

```{r}
network_influence14.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness")
                       + nodemain("Liveness")
                       + nodemain("Speechiness")
                       + nodemain("Key")
                       + nodemain("Duration")
                       + nodefactor("Genre")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm14.fit <- ergm(network_influence14.ergm)
```

```{r}
anova(network_influence.ergm14.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm14.fit)
```

ERGM with characteristics loudness, danceability, energy, valence, tempo, acousticness, instrumentalness, liveness, speechiness, key, duration, start date, genre, genre matching, key matching:

```{r}
network_influence15.ergm <- formula(network_influence ~ edges
                       + nodemain("Loudness")
                       + nodemain("Danceability")
                       + nodemain("Energy")
                       + nodemain("Valence")
                       + nodemain("Tempo")
                       + nodemain("Acousticness")
                       + nodemain("Instrumentalness")
                       + nodemain("Liveness")
                       + nodemain("Speechiness")
                       + nodemain("Key")
                       + nodemain("Duration")
                       + nodemain("ActiveStart")
                       + nodefactor("Genre")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm15.fit <- ergm(network_influence15.ergm)
```


```{r}
anova(network_influence.ergm15.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm15.fit)
```

```{r}
gof.network.ergm15 <- gof(network_influence.ergm15.fit)

plot(gof.network.ergm15)

```

```{r}
gof.network.ergm15
```

