---
title: "ERGM Fitting"
output: ergmfitting
---

Code adapted from Chapter 6 of "Statistical Analysis of Network Data in R" by Kolacsyk and Csardi and https://gvegayon.github.io/appliedsnar/the-ergm-package.html. 

Load necessary packages.

```{r}
library(ergm)
library(intergraph)
```

Convert igraph network "net1" to network object.

```{r}
network_influence <- intergraph::asNetwork(net1)

# Running a simple ergm (only fitting edge count)
ergm(network_influence ~ edges)
```
Add vertex attributes to network graph.

```{r}
network::set.vertex.attribute(network_influence, "Genre",
                              data_by_artist_with_genre$artist_genre)
network::set.vertex.attribute(network_influence, "Danceability",
                              data_by_artist_with_genre$danceability)
network::set.vertex.attribute(network_influence, "Energy",
                              data_by_artist_with_genre$energy)
network::set.vertex.attribute(network_influence, "Loudness",
                              data_by_artist_with_genre$loudness)
network::set.vertex.attribute(network_influence, "Valence",
                              data_by_artist_with_genre$valence)
network::set.vertex.attribute(network_influence, "Tempo",
                              data_by_artist_with_genre$tempo)
network::set.vertex.attribute(network_influence, "Key",
                              data_by_artist_with_genre$key)
network::set.vertex.attribute(network_influence, "Acousticness",
                              data_by_artist_with_genre$acousticness)
network::set.vertex.attribute(network_influence, "Instrumentalness",
                              data_by_artist_with_genre$instrumentalness)
network::set.vertex.attribute(network_influence, "Liveness",
                              data_by_artist_with_genre$liveness)
network::set.vertex.attribute(network_influence, "Speechiness",
                              data_by_artist_with_genre$speechiness)
network::set.vertex.attribute(network_influence, "Duration",
                              data_by_artist_with_genre$duration_ms)
```


Create Bernoulli random graph model.

```{r}
my.ergm.bern <- formula(network_influence ~ edges)
my.ergm.bern
summary(my.ergm.bern)
#degreedist(network_influence)
```


Fit ERGMs using vertex characteristics. Add characteristics individually.

```{r}
network_influence1absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Danceability"))

set.seed(42)
network_influence.ergm1absdiff.fit <- ergm(network_influence1absdiff.ergm)
```
```{r}
anova(network_influence.ergm1absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm1absdiff.fit)
```

```{r}
network_influence2absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Danceability")
                       + absdiff("Energy"))

set.seed(42)
network_influence.ergm2absdiff.fit <- ergm(network_influence2absdiff.ergm)
```

```{r}
anova(network_influence.ergm2absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm2absdiff.fit)
```
```{r}
network_influence3absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy"))

set.seed(42)
network_influence.ergm3absdiff.fit <- ergm(network_influence3absdiff.ergm)
```

```{r}
anova(network_influence.ergm3absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm3absdiff.fit)
```

```{r}
network_influence4absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence"))

set.seed(42)
network_influence.ergm4absdiff.fit <- ergm(network_influence4absdiff.ergm)
```

```{r}
anova(network_influence.ergm4absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm4absdiff.fit)
```

```{r}
network_influence5absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo"))

set.seed(42)
network_influence.ergm5absdiff.fit <- ergm(network_influence5absdiff.ergm)
```
```{r}
anova(network_influence.ergm5absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm5absdiff.fit)
```

```{r}
network_influence6absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness"))

set.seed(42)
network_influence.ergm6absdiff.fit <- ergm(network_influence6absdiff.ergm)
```

```{r}
anova(network_influence.ergm6absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm6absdiff.fit)
```


```{r}
network_influence7absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness"))

set.seed(42)
network_influence.ergm7absdiff.fit <- ergm(network_influence7absdiff.ergm)
```

```{r}
anova(network_influence.ergm7absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm7absdiff.fit)
```


```{r}
network_influence8absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness")
                       + absdiff("Liveness"))

set.seed(42)
network_influence.ergm8absdiff.fit <- ergm(network_influence8absdiff.ergm)
```

```{r}
anova(network_influence.ergm8absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm8absdiff.fit)
```


```{r}
network_influence9absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness")
                       + absdiff("Liveness")
                       + absdiff("Speechiness"))

set.seed(42)
network_influence.ergm9absdiff.fit <- ergm(network_influence9absdiff.ergm)
```

```{r}
anova(network_influence.ergm9absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm9absdiff.fit)
```


```{r}
network_influence10absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness")
                       + absdiff("Liveness")
                       + absdiff("Speechiness")
                       + match("Genre"))

set.seed(42)
network_influence.ergm10absdiff.fit <- ergm(network_influence10absdiff.ergm)
```
```{r}
anova(network_influence.ergm10absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm10absdiff.fit)
```
```{r}
network_influence11absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness")
                       + absdiff("Liveness")
                       + absdiff("Speechiness")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm11absdiff.fit <- ergm(network_influence11absdiff.ergm)
```

```{r}
anova(network_influence.ergm11absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm11absdiff.fit)
```
```{r}
network_influence12absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness")
                       + absdiff("Liveness")
                       + absdiff("Speechiness")
                       + absdiff("Key")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm12absdiff.fit <- ergm(network_influence12absdiff.ergm)
```

```{r}
anova(network_influence.ergm12absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm12absdiff.fit)
```

 

```{r}
network_influence13absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness")
                       + absdiff("Liveness")
                       + absdiff("Speechiness")
                       + nodefactor("Genre")
                       + absdiff("Key")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm13absdiff.fit <- ergm(network_influence13absdiff.ergm)
```

```{r}
anova(network_influence.ergm13absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")
summary(network_influence.ergm13absdiff.fit)
```
Model 13 has lowest AIC of all the absolute difference models. 

```{r}
gof.network.ergm13absdiff <- gof(network_influence.ergm13absdiff.fit)

plot(gof.network.ergm13absdiff)

gof.network.ergm13absdiff

```
Goodness of fit calculations for model 13 show that the p-value for most of our explanatory values is high, indicating a moderately good fit.

```{r}
mcmc.diagnostics(network_influence.ergm13absdiff.fit)
```


```{r}
network_influence15absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness")
                       + absdiff("Liveness")
                       + absdiff("Speechiness")
                       + nodematch("Key"))

set.seed(42)
network_influence.ergm15absdiff.fit <- ergm(network_influence15absdiff.ergm)
```
```{r}
anova(network_influence.ergm15absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm15absdiff.fit)
```
Worse than model 13--do not use!
```{r}
gof.network.ergm15d <- gof(network_influence.ergm15d.fit)

plot(gof.network.ergm15d)
```
```{r}
network_influence16absdiff.ergm <- formula(network_influence ~ edges
                       + absdiff("Loudness")
                       + absdiff("Danceability")
                       + absdiff("Energy")
                       + absdiff("Valence")
                       + absdiff("Tempo")
                       + absdiff("Acousticness")
                       + absdiff("Instrumentalness")
                       + absdiff("Liveness")
                       + absdiff("Speechiness")
                       + match("Key")
                       + match("Genre"))

set.seed(42)
network_influence.ergm16absdiff.fit <- ergm(network_influence16absdiff.ergm)
```


```{r}
anova(network_influence.ergm16absdiff.fit, eval.loglik = TRUE, scale = 0, test = "F")

summary(network_influence.ergm16absdiff.fit)
```

```{r}
gof.network.ergm16d <- gof(network_influence.ergm16d.fit)

plot(gof.network.ergm16d)
```

