---
title: "Music Network Model Data Import"
output: html_notebook
---
In this notebook, we import data, clean it, and create the network graph that will be used for analyzing data throughout the project.

Load necessary packages.

```{r}
library(igraph)
library(Hmisc)
```

Import data into R. Note: Users must change directory to reflect correct file path.

```{r}
full_music_data <- read.csv("~/Documents/Documents - Elizabeth’s MacBook Pro (6321)/Github/musicnetworkanalysis/ICM Problem Data/full_music_data.csv")
View(full_music_data)

influence_data <- read.csv("~/Documents/Documents - Elizabeth’s MacBook Pro (6321)/Github/musicnetworkanalysis/ICM Problem Data/influence_data.csv")
View(influence_data)

data_by_artist <- read.csv("~/Documents/Documents - Elizabeth’s MacBook Pro (6321)/Github/musicnetworkanalysis/ICM Problem Data/data_by_artist.csv")
View(data_by_artist)

data_by_year <- read.csv("~/Documents/Documents - Elizabeth’s MacBook Pro (6321)/Github/musicnetworkanalysis/ICM Problem Data/data_by_year.csv")
View(data_by_year)
```

Reorder columns and remove unnecessary columns from influence data.

```{r}
colnames(influence_data)
influence2 <- influence_data[, c(1, 5, 2, 3, 4, 6, 7, 8)]
View(influence2)
```
Import data that has combined artist data with genre data from influence data.

```{r}
data_by_artist_with_genre <- read.csv("~/Documents/Documents - Elizabeth’s MacBook Pro (6321)/Github/musicnetworkanalysis/ICM Problem Data/data_by_artist_with_genre.csv")
View(data_by_artist_with_genre)
```

